---
title: "Simulation Testing Data Limited Methods"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
github_document:
  mathjax: TRUE
html_document:
  fig_width: 6 
  fig_height: 4 
tags: [FLR]
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---
 
 i) set up an OM, 
 ii) use an OEM to generate length data, 
 iii) estimate empirical LBIs, 
 iv) simple model based estimates using FLR 
 v) wrappers for 3rd party methods
 vi) evaluate robustness to uncertainty
 
```{r, ini, echo=FALSE, results='hide', message=FALSE, warnings=FALSE, cache=FALSE,eval=!TRUE}
library(knitr)
source("../R/ini.R")
```

```{r knitr_init, echo=FALSE, results="hide", eval=!FALSE}
library(knitr)
## Global options
opts_chunk$set(cache     =!TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="tex",
               cache.path="cache")
```

```{r}
options(digits=3)

iFig=0
```


# Introduction

This tutorial describes how to simuation test data limited methods in `FLR` using a variety of other packages.

## Required packages

To follow this tutorial you should have installed the following packages:

- FLR: [FLCore](http://www.flr-project.org/FLCore/), [FLBRP](http://www.flr-project.org/FLBRP/), [FLasher](http://www.flr-project.org/FLash/), [FLife](http://www.flr-project.org/FLife/)

for example

```{r, install, eval=FALSE}
install.packages(c("FLCore"),  repos="http://flr-project.org/R")
install.packages(c("FLBRP"),   repos="http://flr-project.org/R")
install.packages(c("FLasher"), repos="http://flr-project.org/R")
install.packages(c("FLife"),   repos="http://flr-project.org/R")
```

```{r, pkgs}
# Load  packages
library(ggplot2)
library(plyr)
library(reshape)

library(FLCore)
library(ggplotFL)
library(FLBRP)
library(FLasher)
library(FLife)

library(MLZ)
```

# Operating Model

Turbot

```{r, turbot}
lh=FLPar(c(linf= 59.1,  k=0.28, t0=-0.4, a=0.01111,b=3.15,a50=4.0, l50=43.25),units="NA")
lh=lhPar(lh)
eq=lhEql(lh)

gTime=c(round(mydas:::gt(eq)))
fbar(eq)=refpts(eq)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                              seq(.1,2,length.out=30)[-30],
                                              seq(2,1.0,length.out=gTime)[-1],
                                              rep(1.0,61)))[,1:105]

om=as(eq,"FLStock")
om=fwd(om,f=fbar(om)[,-1], sr=eq)
```

```{r turbot-ts-ref}
plot(FLQuants(om, 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"],
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"])) + 
  geom_hline(aes(yintercept=1),col="red",linetype=2)+
  theme_bw() 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.

# Length Based Methods


Based on Beverton and Holt  $L_{F} = \frac{L\infty +\frac{F+M}{K}L_c}{1+\frac{F+M}{K}}$

+ $L_{current}/L_{F=M}$ 
+ $M/(Z_{current}-M)$
+ $F_{0.1}/(Z_{current}-M)$
+ $LBSPR$ Length-based spawning potential ratio (Hordyk et al. 2015) 
+ $Lime$ (Rudd and Thorson, 2018) mixed effects non-equilibrium



## MLZ

[MLZ](https://cran.r-project.org/web/packages/MLZ/index.html) is a package that facilitates data preparation and estimation of mortality with statistical diagnostics using the mean length-based mortality estimator and several extensions.


```{r}
library(MLZ)

library(popbio)
```

```{r, turbot-length}
#source('~/Desktop/flr/mydas/R/omOut.R')

ts   =mydas:::omSmry(om,eq,lh)
mnLen=as.FLQuant(with(ts,data.frame(data=cln,year=year,iter=iter)))

plot(mnLen)
```
**Figure `r iFig=iFig+1; iFig`** Mean length of catch turbot. 

```{r}
#source('~/Desktop/flr/mydas/R/popdyn.R')
#growth<-vonB
prior=mydas:::popdyn(lh)
```

```{r, turbot-mlz}
source('../R/mlz.R')

res=mlz(mnLen[,ac(40:60)],prior)

res
```


## LB-SPR

[LBSPR](https://cran.r-project.org/web/packages/LBSPR/vignettes/LBSPR.html)
is a R package for simulation and estimation using life-history ratios and length composition data


```{r lbspr}
library(LBSPR)
```

```{r, turbot-alk}
source("../R/oemLn.R")
ak=invAlk(lh)  
```

```{r}
save(ak,file="ak.RData")
```

```{r, turbot-lfd}
lfd=lenSample(catch.n(om)[,20:65],ak,nsample=500)
```


```{r, turbot-oemplot}
ggplot(melt(lfd[,seq(1,45,10)]))+
  geom_histogram(aes(len,weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```

**Figure `r iFig=iFig+1; iFig`** Observation error model for turbot. 



```{r, turbot-sa}
library(LBSPR)
library(mydas)
library(popbio)

#growth=vonB

prior=popdyn(lh)
source("../R/lbspr.R")

lb=lbspr(lfd,prior)  
```


```{r, turbot-spr}
ggplot(melt(sweep(lb[["spr"]],c(1,3),lb[["spr"]][,"40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  ylab("SPR")+xlab("Year")+theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Estimates of SPR for turbot. 

```{r, turbot-fm}
ggplot(melt(sweep(lb[["fm"]],c(1,3),lb[["fm"]][,"40"],"/")))+
  geom_boxplot(aes(ac(year),value))+
  scale_x_discrete(breaks=seq(20,60,10))+
  ylab("F")+xlab("Year")+theme_bw()
```

**Figure `r iFig=iFig+1; iFig`** Estimates of $F/M$ for turbot. 


# Estimation {#Estimation}

Life history parameters can also be used to estimate quantities of use in stock assessment

@beverton1956review developed a method to estimate life history and population parameters length data. e.g. 

\begin{equation}Z=K\frac{L_{\infty}-\overline{L}}{\overline{L}-L^\prime} \end{equation}
Based on which @powell1979estimation developed a method, extended by @wetherall1987estimating, to estimate growth and mortality parameters. This assumes that the right hand tail of a length frequency distribution was determined by the asymptotic length $L_{\infty}$ and the ratio between Z and the growth rate k. 

The Beverton and Holt methods assumes good estimates for K and $L_{\infty}$, while the Powell-Wetherall method only requires an estimate of K, since $L_{\infty}$ is estimated by the method as well as Z/K.These method therefore provide estimates for each distribution of Z/K, if K is unknown and Z if K is known.  
%As well as assuming that growth follows the von Bertalanffy growth function, it is also assumed that the population is in a steady state with constant exponential mortality, no changes in selection pattern of the fishery and constant recruitment. In the Powell-Wetherall method $L^\prime$ can take any value between the smallest and largest sizes. Equation 1 then provides a series of estimates of Z and since 

\begin{equation}\overline{L}-L^\prime=a+bL^{\prime} \end{equation}
 a and b can be estimated by a regression analysis where 
\begin{equation}b=\frac{-K}{Z+K} \end{equation}
 \begin{equation}a=-bL_{\infty} \end{equation}
Therefore plotting $\overline{L}-L^\prime$ against $L^\prime$ therefore provides an estimate of $L_{\infty}$ and Z/K

Plotting $\overline{L}-L^\prime$ against $L^\prime$ provides an estimate of $L_{\infty}$ and Z/k, since $L_{\infty}=-a/b$ and $Z/k=\frac{-1-b}{b}$. If k is known then it also provides an estimate of Z (\textbf{Figure} \ref{fig:15}).

```{r}
source("../R/cc.R")

data(ple4)
ctc=as.data.frame(catch.n(ple4))
dat=cc(age=ctc$age,n=ctc$data)
head(dat)
```


```{r}
load("../data/cas.RData")
source("../R/powh.R")

pw=ddply(subset(cas), .(year), 
   function(cas) powh(cas$len,cas$n)$data)
   
   pw=transform(pw, lustrum=(year%/%5)*5,
         yr    =year-(year%/%5)*5,
         weight=ifelse(len>=100&len<=200,1,0))
         
ggplot(pw)+
   geom_line(aes(len,diff,colour=factor(yr),group=year))+
   scale_x_continuous(limits=c(0,300)) +
   xlab("Length (cm)")+
   ylab("Difference between Length and Mean Size")+
   geom_smooth(aes(len,diff,weight=weight),
   method="lm",col="red",size=1.25,alpha=.1)+
   theme_bw()+theme(legend.position="none")
```

### Catch curve analysis
```{r, echo=TRUE}
data(ple4)
ctc=as.data.frame(catch.n(ple4))
ctc=ddply(ctc,.(year), with, cc(age=age,n=data))
ctc=ddply(transform(ctc,decade=factor(10*(year%/%10))),.(decade,age),with,data.frame(sel=mean(sel)))
ggplot(ctc)+
  geom_line(aes(age,sel,colour=decade))
```


# References

# More information

* You can submit bug reports, questions or suggestions on this tutorial at <https://github.com/flr/doc/issues>.
* Or send a pull request to <https://github.com/flr/doc/>
* For more information on the FLR Project for Quantitative Fisheries Science in R, visit the FLR webpage, <http://flr-project.org>.

## Software Versions

* `r version$version.string`
* FLCore: `r packageVersion('FLCore')`
* FLasher: `r packageVersion('FLasher')`
* **Compiled**: `r date()`

## License

This document is licensed under the [Creative Commons Attribution-ShareAlike 4.0 International](https://creativecommons.org/licenses/by-sa/4.0) license.

## Author information

**Laurence KELL**. laurie@seaplusplus.co.uk


## Acknowledgements

This vignette and the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.
