---
title: "test"
author: "Pierucci"
date: "1/12/2021"
output: html_document
---
 i) Conduct a length-based assessment
 ii) Set up an OM, 
 iii) use an OEM to generate length data, 
 iv) estimate empirical LBIs, 
 v) simple model based estimates using FLR 
 vi) wrappers for 3rd party methods
 vii) evaluate robustness to uncertainty
 
```{r, ini, echo=FALSE, results='hide', message=FALSE, warnings=FALSE, cache=FALSE,eval=!TRUE}
library(knitr)
source("C:/Users/andre/OneDrive/Desktop/ini.R")
```

```{r knitr_init, echo=FALSE, results="hide", eval=!FALSE}
library(knitr)
## Global options
opts_chunk$set(cache     =!TRUE,
               echo      =FALSE,
               eval      =TRUE,
               prompt    =FALSE,
               comment   =NA,
               message   =FALSE,
               warning   =FALSE,
               tidy      =TRUE,
               fig.height=6,
               fig.width =8,
               fig.path  ="tex/simtest/len-",
               cache.path="cache/simtest/len/")
```

```{r}
options(digits=3)
iFig=0
```


# Introduction

This vignettel conducts an initial length based assessment for sea urchin, then sets up a simulation model to test data limited methods in `FLR` 

## Required packages

To follow this tutorial you should have installed the following packages:

- FLR: [FLCore](http://www.flr-project.org/FLCore/), [FLBRP](http://www.flr-project.org/FLBRP/), [FLasher](http://www.flr-project.org/FLash/), [FLife](http://www.flr-project.org/FLife/)

for example

```{r, install, eval=FALSE}
#install.packages(c("FLCore"),  repos="http://flr-project.org/R")
#(c("FLBRP"),   repos="http://flr-project.org/R")
#install.packages(c("FLasher"), repos="http://flr-project.org/R")
#install.packages(c("FLife"),   repos="http://flr-project.org/R")
```

```{r, pkgs}
# Load  packages
library(ggplot2)
library(plyr)
library(reshape)
library(FLCore)
library(ggplotFL)
library(FLBRP)
library(FLasher)
library(FLife)

library(mydas)
library(popbio)

library(LBSPR)

source("../R/lbspr.R")
```


# Length Based Methods

Based on Beverton and Holt  $L_{F} = \frac{L\infty +\frac{F+M}{K}L_c}{1+\frac{F+M}{K}}$

+ $LBSPR$ Length-based spawning potential ratio (Hordyk et al. 2015) 


## LB-SPR

[LBSPR](https://cran.r-project.org/web/packages/LBSPR/vignettes/LBSPR.html)
is a R package for simulation and estimation using life-history ratios and length composition data



```{r lbspr}
library(LBSPR)
```

```{r, urchin-alk}
lh=FLPar(c(linf=130,  k=0.5, t0=-0.1, a=0.0003,b=3.000,a50=1.5353 , l50=66.5733 ),units="mm")

ak=invAlk(lh)  
```

```{r, urchin-lfd}
library(reshape)

lfd=read.csv("../inputs/commercial_S.csv", row.names=NULL)

names(lfd)=c("len",substr(names(lfd)[-1],2,5))

lfd=as.FLQuant(with(melt(lfd,id="len"),data.frame(length=len,year=variable,data=value)))[,names(lfd)[-1]]

ggplot(melt(lfd))+
  geom_histogram(aes(length, weight=value),binwidth=1)+
  facet_grid(year~iter,scale="free")+
  xlab("Length (cm)")+ylab("Frequency")+
  coord_cartesian(xlim=c(0,mean(lh["linf"])))
```

**Figure `r iFig=iFig+1; iFig`** Length data for urchin. 


```{r, urchin-sa}
library(ggplotFL)
library(FLife)
library(mydas)
library(popbio)

library(plyr)
library(LBSPR)

source("../R/lbspr.R")
lh=FLPar(c(linf=130,  k=0.5, t0=-0.1, a=0.0003,b=3.000,a50=1.5353 , l50=66.5733 ),units="mm")

prior=popdyn(lh)

lb=lbspr(lfd,prior)  
```


```{r, urchin-plot}
plot(lb)
```

**Figure `r iFig=iFig+1; iFig`** Estimates for urchin. 


# Operating Model

urchin

```{r, urchin}
lh=FLPar(c(linf= 130,  k=0.5, t0=-0.1, a=0.0003,b=3.000,a50=1.5353 , l50=66.5733 ),units="mm")
lh=lhPar(lh)
eq=lhEql(lh)
gTime=5 #c(round(mydas:::gt(eq)))
fbar(eq)=refpts(eq)["msy","harvest"]%*%FLQuant(c(rep(.1,19),
                                              seq(.1,2,length.out=30)[-30],
                                              seq(2,1.0,length.out=gTime)[-1],
                                              rep(1.0,61)))[,1:105]
om=as(eq,"FLStock")
om=fwd(om,f=fbar(om)[,-1], sr=eq)

```

```{r urchin-ts-ref}
plot(FLQuants(om, 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"],
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"])) + 
  geom_hline(aes(yintercept=1),col="red",linetype=2)+
  theme_bw() 
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.
